### 2015-06-24 paper.tex
- Added some things to the introduction and results part. - Applied some minor changes suggested by Sebastian.

\documentclass[runningheads,a4paper]{llncs}

\usepackage[utf8]{inputenc}

\usepackage{url}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{amsmath} 
\usepackage{caption}
\usepackage[]{algorithm2e}
\usepackage{todonotes}
\usepackage{listings}
\usepackage{multirow}
\usepackage{enumitem}

\usepackage{lipsum}
\usepackage{todonotes}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\usepackage{listings}
\lstset{numbers=left,numbersep=4pt,numberstyle=\tiny\colour{gray}, basicstyle=\ttfamily\footnotesize, tabsize=2, framexleftmargin=2pt, captionpos=b, frame=none,framerule=0pt, breaklines=true, showspaces=false,showtabs=false, keywordstyle=\colour{white}, morekeywords={lemon:,lexinfo:}}

\begin{document}

\mainmatter  % start of an individual contribution

\newcommand{\acronym}{V-SEL}

%opening
\title{Vector-Similarity based Entity Linking}
\titlerunning{Vector-Similarity based Entity Linking}

\author{Felix Tristram \and Sebastian Walter \and Philipp Cimiano}
\authorrunning{Felix Tristram \and Sebastian Walter \and Philipp Cimiano}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Semantic Computing Group, CITEC, Bielefeld University}

\maketitle

\begin{abstract}

\keywords{Ontology lexicalization, DBpedia, \acronym{}}
\end{abstract}

\section{Introduction}\label{sec:introduction}
Entity linking belongs to the field of natural language processing and is concerned with determining the identity of entities mentioned in a text. Note that entity linking is not concerned with recognizing a person as a person or a name as a name -- such a practice is the concern of a task known as named-entity recognition. Entity linking only refers to creating an association between a token in some form of input with the representation of an entity in some knowledge base.

\todo{Write introduction}

\section{Approach}\label{sec:approach}
The input data for {\acronym} is a regular piece of text, for example a newspaper article (further referred to simply as \textit{input}), in which entity-representing fragments are already identified (possibly by named-entity recognition software). A fragment from a given text is a token, or multiple successive tokens, which are representing the same entity. For a given fragment the algorithm is supposed to determine the matching real world entity. In order to do so, a set of entity candidates for this fragment is needed, of which the algorithm has to pick the one which is most likely correct.

A fragment which represents a real world entity is called an anchor. To gather a database of anchors and their corresponding entities, data was extracted directly from a Wikipedia XML dump\footnote{More information on downloading Wikipedia dumps here: \url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}}. In these dumps a hyperlink to another page appears together like so:\\
\centerline{\tt{[[Barack Obama|President Obama]]}}\\
where {\textit{Barack Obama} refers to an entity\footnote{\url{http://en.wikipedia.org/wiki/Barack_Obama}} and \textit{President Obama} is the anchor string which appears in the page's text. A map is generated by parsing all Wikipedia articles (in a chosen language) and counting the occurrences of anchor-entity pairs. This map is the foundation for finding all applicable candidates for a given fragment.

Choosing one candidate over an other is achieved by computing a score for each candidate using four components:

The \textbf{tf--idf vector similarity} measures how similar the input is to the abstract of the candidate's Wikipedia entry with regards to the words which appear in both texts. The tf--idf value for a word reflects how important it is in a document, therefore if there is a large overlap between the important words in the input and the abstract of a candidate's Wikipedia page, the candidate is considered to be more likely correct.

The tf--idf vector for each entity is generated by picking the 100 (top 100 was an arbitrary choice to limit the maximal size of each datum) terms from its Wikipedia page's abstract $a$ with the highest tf--idf score. To calculate this score for a term $t$ its tf and idf values are needed. The tf value can be obtained by simply counting all occurrences of $t$ in $a$. The idf value can be obtained by treating the set of all entities' abstracts as the corpus and computing the idf score for every occurring word.

The \textbf{semantic signature vector similarity} measures the overlap between the candidate's \textbf{semantic signature} (see Chapter \ref{subsec:semsig}) and the set of all candidates for the input. It stands to reason that a candidate is more likely to be the correct assignment for a given fragment if entities from its semantic signature are considered for other fragments (as related entities probably appear together).

To account for how often an anchor refers to a given entity the \textbf{candidate reference probability} is incorporated into the score calculation. Using the word \textit{Michelangelo} as an anchor we might receive as candidates Michelangelo the Renaissance artist/engineer\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo}} and Michelangelo the Ninja Turtle\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo_(Teenage_Mutant_Ninja_Turtles)}}. While both are valid candidates worthy of consideration, we can extract from Wikipedia that \textit{Michelangelo} referred only 21 times to the Ninja Turtle, but 1173 times to the artist. Turning these candidate reference frequencies into probabilities (dividing by the total number of fragment-entity links) we can use them as a factor when calculating the score for a candidate.

Another variable used to increase scores for more `important' entities is their \textbf{PageRank}. Applying the same algorithms used by Google around the new millennium we can calculate a PageRank for each entity in the interlinked graph of Wikipedia entries.

Note that all four components can be precomputed for each entity known to the system, which means only few computations have to be done during runtime.

\todo{Write tansition to component explanation}

\subsection{Semantic signature vector}\label{subsec:semsig}
The semantic signature for an entity is computed as described in \cite{Babelfy}, but for the graph of interlinked Wikipedia pages (each page is a vertex, each link between pages is an edge) instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base. The idea is to identify for each page all other pages it is closely related to. This is a two step process:

First, the edges will be assigned weights so that edges in denser parts of the graph become more important. The weight of an edge $\mathrm{weight}(v, v')$ is the number of directed triangles (directed cycles of length 3) it appears in:
$$\mathrm{weight}(v, v') := |\{(v, v', v'') : (v, v'), (v', v''), (v'', v) \in E\}| + 1$$

where $v$, $v'$ and $v''$ are vertices and $E$ is the set of all the graph's edges.

Second, random walks with restart are performed from each vertex (a random walk is a path that consists of succession of random steps). For a number of $n$ steps\footnote{100.000 in this implementation. More would have not been computable in a reasonable time.} the graph is explored by `walking' to a connected vertex with probability $1 - \alpha$ or to move back to the vertex of origin with probability $\alpha$. The probability of visiting the vertex $v'$ is based on the normalized weight of the connecting edge:
$$P(v'|v) = \frac{\mathrm{weight}(v, v')}{\sum _{v''\in V} \mathrm{weight}(v, v'')}$$
where V is the set of all vertices in the graph.

During the random walk for a given root vertex $v_r$, the visits to each vertex $v_i (i \neq r)$ are counted. The result is a frequency distribution of related vertices in which the vertices with the higher counts are interpreted as to be more relevant to the root vertex than vertices with lower counts. Vertices with a count lower than threshold $\tau$ are ignored\footnote{$\tau = 10$ for this implementation, so that $n$ and $\tau$ have the same ratio as in \cite{Babelfy}.}.

\subsection{PageRank}\label{sec:pagerank}
The idea behind the PageRank\cite{pageRank} algorithm was to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question. As Wikipedia entries form a highly interconnected graph the same principle can be applied to them to determine the page rank of an entity local to Wikipedia.

Let $u$ be a web page. $B_u$ is the set of pages that have a hyperlink pointing to $u$. Let $N_u$ be the number of outgoing links for page $u$. A slightly simplified PageRank is then defined as such: 
$$R(u) = c \sum_{v \in B_u} \frac{R(v)}{N_v}$$
where $c$ is a normalizing factor. Notably the PageRank of a page is derived from the PageRank of its incoming links, meaning that the algorithm has to be iterated until the system reaches a steady state. The overall PageRank for a graph is supposed to be constant, but there are corner cases (like cycles) that have to be accounted for. 
%See \cite{pageRank} for more information.

%\subsection{On-line calculation}
%
%This chapter describes the calculations that have to performed by the system during runtime.

\subsection{Finding the eligible candidates}
Since multi-token fragments are already explicitly noted in the used data sets (see Chapter \ref{sec:dataset}), {\acronym} uses a simplified algorithm for candidate identification. Candidate scoring, instead of sophisticated fragment and candidate identification, was the focus of the development of {\acronym}. But {\acronym} would undeniably benefit from an in-depth fragment recognizer and candidate identifier.

Tokens that are not part of a hand-annotated fragment, as well as single- or multi-token expressions from fragments, are simply looked up in the set of known anchors to determine their candidates. This works quite well for straightforward annotations like $Red\ Bull \rightarrow Red\_Bull$ (as it might appear in the AIDA data set), but is problematic with more obscure annotations like $Red\ Bull \rightarrow FC\_Red\_Bull\_Salzburg$ (as it might appear in the KORE50 data set).

\subsection{Semantic signature vector for input}\label{subsection:semSigVector}
To calculate the similarity score for each candidate, their semantic signature vector needs to compared to the semantic signature vector of the input. Unfortunately, the input does not have a semantic signature of its own. As a surrogate a candidate vector is generated as such: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$. For each candidate-entity of every fragment, check whether it already appears in the mapping. If not, add it to the map and set its count to one. If it exists, increment its count by one.

Therefore a candidate's semantic signature similarity score increases as entities from their semantic signature appear more often as candidates in a given input (see Chapter \ref{subsec:VectorEvaluation} for the implementation).

\subsection{tf--idf vector for input}\label{subsec:tfidfInput}
The tf--idf vector for the input is calculated in the same fashion as for the candidates. The term frequency for every term in the input is found by counting all its occurrences, and its inverse document frequency is looked up in the idf map that was generated in Chapter \ref{sec:offlineTFIDF}. Terms that are unique to the input are ignored, as they do not affect the entity's vector score (they are multiplied by zero in the vector similarity calculation -- see Chapter \ref{sec:score computation}).

\subsection{Score computation}\label{sec:score computation}
The cosine similarity between the vectors $A$ and $B$ is calculated as follows
$$\mathrm{similarity}(A, B) = \cos(\theta) = \frac{A \cdot B}{\|A\| \|B\|}$$

There will be two similarity scores for each candidate:
\begin{enumerate}
\item The similarity $s_{\text{tf--idf}}$ between the tf--idf vectors of the input and the candidate.
\item The similarity $s_{\text{semsig}}$ between the candidate vector of the input and the semantic signature vector of the candidate.
\end{enumerate}

\section{Results}\label{sec:results}

\begin{table}
\centering
\caption{Highest accuracy reached by {\acronym}, Babelfy, and DBpedia Spotlight.}
\label{table:redirects}
\begin{tabular}{ | c | c | c | c |}
    \hline
    & {\acronym} & Babelfy & DBpedia Spotlight \\ \hline
    AIDA & x\% & 66.42\%* & 49.41\%\\ \hline
    KORE50 & x\% & 47.89\% & x\%\\ \hline
\end{tabular}
\end{table}
\section{Conclusion}\label{sec:conclusion}
The experiments have shown that {\acronym} is viable approach for entity linking. On the AIDA dataset, {\acronym} performs comparably to Babelfy and better than DBpedia Spotlight. On the KORE50 dataset however Babelfy reaches a higher accuracy than {\acronym}. KORE50 was built intentionally to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic signature vector overlaps.

{\acronym} is very fast. Evaluating the full KORE50 dataset took about 15 minutes using the Babelfy algorithm, but less than one minute with {\acronym}. Evaluation of the AIDA dataset had to be stopped after 164 hours using the Babelfy algorithm. {\acronym} evaluates the same dataset in about 45 seconds. Since the entity identifier used in this approach tries to find candidates for every token in a text, the graphs used for the Babelfy evaluation become very large, which increases evaluation time. DBpedia Spotlight was not compared with respects to speed as it was not evaluated locally.

{\acronym} works best when a fragment refers to the most common meaning of a word. For example, assignments like \textit{BSE $\rightarrow$ Bovine\_spongiform\_encephalopathy} or \textit{Franz Fischler $\rightarrow$ Franz\_Fischler} are usually correct. More ambiguous fragments get assigned correctly as well when that assignment is the most common one in the given context, for example \textit{commission $\rightarrow$ European\_Commission} in a debate of the European Parliament. Problems arise when the sought after entity is not the most common assignment for a given fragment. For example, the fragment \textit{Spanish} in \textit{Spanish Farm Minister Loyola de Palacio had earlier...} receives the assignment \textit{Spanish $\rightarrow$ Spanish\_Language}, as that token usually refers to the language. But the requested assignment was \textit{Spanish $\rightarrow$ Spain}. This particular kind of case can be avoided by introducing syntactic information to the system, for example by using an automated part of speech tagger. Using syntactic data would prevent the system of assigning a noun to an adjective-fragment.

\bibliographystyle{plain}
\bibliography{biblio}

\end{document}

### 2015-07-07 paper.tex
- reworked the approach section

@@
 
-\todo{Write introduction}
+\todo[inline]{Write introduction}
 
@@
 The input data for {\acronym} is a regular piece of text, for example a newspaper article (further referred to simply as \textit{input}), in which entity-representing fragments are already identified (possibly by named-entity recognition software).
-A fragment from a given text is a token, or multiple successive tokens, which are representing the same entity.
+A \textit{fragment} from a given text is a token, or multiple successive tokens, which are representing the same entity.
 For a given fragment the algorithm is supposed to determine the matching real world entity.
-In order to do so, a set of entity candidates for this fragment is needed, of which the algorithm has to pick the one which is most likely correct.
+In order to do so, a set of entity \textit{candidates} for this fragment is needed, of which the algorithm has to pick the most likely correct one.
 
-A fragment which represents a real world entity is called an anchor.
+A fragment which represents a real world entity is called an \textit{anchor}.
 To gather a database of anchors and their corresponding entities, data was extracted directly from a Wikipedia XML dump\footnote{More information on downloading Wikipedia dumps here: \url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}}.
@@
 A map is generated by parsing all Wikipedia articles (in a chosen language) and counting the occurrences of anchor-entity pairs.
-This map is the foundation for finding all applicable candidates for a given fragment.
+The candidates for a given fragment are now found by looking up all entities that were referred to by the fragment within Wikipedia.
 
-Choosing one candidate over an other is achieved by computing a score for each candidate using four components:
+Candidates are scored by a support vector machine.
+\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four parameters are computed for each candidate, which are used as input for the SVM: tf--idf vector similarity, semantic signature vector similarity, candidate reference probability, and page rank.
 
+% ------------ tf--idf vector similarity -------------------
+\subsection{tf-idf Vector Similarity}
 The \textbf{tf--idf vector similarity} measures how similar the input is to the abstract of the candidate's Wikipedia entry with regards to the words which appear in both texts.
 The tf--idf value for a word reflects how important it is in a document, therefore if there is a large overlap between the important words in the input and the abstract of a candidate's Wikipedia page, the candidate is considered to be more likely correct.
+It calculated from the term frequency (tf) and inverse document frequency (idf).
+$\mathrm{tf}(t, d)$ is the raw frequency of term $t$ in document $d$.
+$\mathrm{idf}(t, D) $ is defines as such:
 
-The tf--idf vector for each entity is generated by picking the 100 (top 100 was an arbitrary choice to limit the maximal size of each datum) terms from its Wikipedia page's abstract $a$ with the highest tf--idf score.
-To calculate this score for a term $t$ its tf and idf values are needed.
+$$\mathrm{idf}(t, D) = \mathrm{log}\frac{N}{|{d \in D : t \in d}|}$$
+
+where $N$ is the number of documents in the corpus and $|{d \in D : t \in d}|$ is the number of documents $t$ appears in. The tf-idf value is the product of the two:
+
+$$ \mathrm{tfidf}(t, d, D) = \mathrm{tf}(t, d) \times \mathrm{idf}(t, D) $$
+
+The tf--idf vector $A$ for each entity is generated by picking the 100 (top 100 was an arbitrary choice to limit the maximal size of each datum) terms from its Wikipedia page's abstract $a$ with the highest tf--idf score.
 The tf value can be obtained by simply counting all occurrences of $t$ in $a$.
@@
 
-The \textbf{semantic signature vector similarity} measures the overlap between the candidate's \textbf{semantic signature} (see Chapter \ref{subsec:semsig}) and the set of all candidates for the input.
+The tf--idf vector for the input $B$ is calculated in the same fashion as for the candidates.
+The term frequency for every term in the input is found by counting all its occurrences in the input text, and its inverse document frequency computed the same way as for each entity.
+Terms that are unique to the input are ignored, as they do not affect the entity's vector score (they are multiplied by zero in the vector similarity calculation).
+
+The tf--idf vector similarity is then calculated as the cosine similarity between vectors $A$ and $B$:
+$$\mathrm{tfidfVectorSimilarity}(A, B) = \cos(\theta) = \frac{A \cdot B}{\|A\| \|B\|}$$
+
+% ------------ semantic signature vector similarity -------------------
+\subsection{Semantic Signature Vector Similarity}
+The \textbf{semantic signature vector similarity} measures the overlap between the candidate's \textbf{semantic signature} and the set of all candidates for the input.
 It stands to reason that a candidate is more likely to be the correct assignment for a given fragment if entities from its semantic signature are considered for other fragments (as related entities probably appear together).
 
-To account for how often an anchor refers to a given entity the \textbf{candidate reference probability} is incorporated into the score calculation.
-Using the word \textit{Michelangelo} as an anchor we might receive as candidates Michelangelo the Renaissance artist/engineer\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo}} and Michelangelo the Ninja Turtle\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo_(Teenage_Mutant_Ninja_Turtles)}}.
-While both are valid candidates worthy of consideration, we can extract from Wikipedia that \textit{Michelangelo} referred only 21 times to the Ninja Turtle, but 1173 times to the artist.
-Turning these candidate reference frequencies into probabilities (dividing by the total number of fragment-entity links) we can use them as a factor when calculating the score for a candidate.
-
-Another variable used to increase scores for more `important' entities is their \textbf{PageRank}.
-Applying the same algorithms used by Google around the new millennium we can calculate a PageRank for each entity in the interlinked graph of Wikipedia entries.
-
-Note that all four components can be precomputed for each entity known to the system, which means only few computations have to be done during runtime.
-
-\todo{Write tansition to component explanation}
-
-\subsection{Semantic signature vector}\label{subsec:semsig}
 The semantic signature for an entity is computed as described in \cite{Babelfy}, but for the graph of interlinked Wikipedia pages (each page is a vertex, each link between pages is an edge) instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base.
@@
 The probability of visiting the vertex $v'$ is based on the normalized weight of the connecting edge:
-$$P(v'|v) = \frac{\mathrm{weight}(v, v')}{\sum _{v''\in V} \mathrm{weight}(v, v'')}$$
+$$P(v'|v) = \frac{\mathrm{weight}(v, v')}{\sum\limits_{v''\in V} \mathrm{weight}(v, v'')}$$
 where V is the set of all vertices in the graph.
@@
 
-\subsection{PageRank}\label{sec:pagerank}
+To calculate the similarity score for each candidate, their semantic signature vector needs to compared to the semantic signature vector of the input.
+Unfortunately, the input does not have a semantic signature of its own.
+As a surrogate a candidate vector is generated as such: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$.
+For each candidate-entity of every fragment, check whether it already appears in the mapping.
+If not, add it to the map and set its count to one.
+If it exists, increment its count by one.
+
+Therefore a candidate's semantic signature similarity score increases as entities from their semantic signature appear more often as candidates in a given input.
+
+% ------------ candidate reference probability -------------------
+\subsection{Candidate Reference Probability}
+To account for how often an anchor refers to a given entity the \textbf{candidate reference probability} is incorporated into the score calculation.
+Using the word \textit{Michelangelo} as an anchor we might receive as candidates Michelangelo the Renaissance artist/engineer\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo}} and Michelangelo the Ninja Turtle\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo_(Teenage_Mutant_Ninja_Turtles)}}.
+While both are valid candidates worthy of consideration, we can extract from Wikipedia that \textit{Michelangelo} referred only 21 times to the Ninja Turtle, but 1173 times to the artist.
+Turning these candidate reference frequencies into probabilities (dividing by the total number of references towards a given entity) we can use them as a factor when calculating the score for a candidate:
+
+$$\mathrm{crp}(a, e) := \frac{\mathrm{ref}(a, e)}{{\sum\limits_{a'\in E} \mathrm{ref}(a', e)}}$$
+
+where $\mathrm{ref}(a, e)$ is the number of references from anchor/candidate $a$ to entity $e$ and $E$ is the set of all anchors referring to $e$.
+
+% ------------ page rank -------------------
+\subsection{Page Rank}
 The idea behind the PageRank\cite{pageRank} algorithm was to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
@@
 The overall PageRank for a graph is supposed to be constant, but there are corner cases (like cycles) that have to be accounted for.
-%See \cite{pageRank} for more information.
-
-%\subsection{On-line calculation}
-%
-%This chapter describes the calculations that have to performed by the system during runtime.
-
-\subsection{Finding the eligible candidates}
-Since multi-token fragments are already explicitly noted in the used data sets (see Chapter \ref{sec:dataset}), {\acronym} uses a simplified algorithm for candidate identification.
-Candidate scoring, instead of sophisticated fragment and candidate identification, was the focus of the development of {\acronym}.
-But {\acronym} would undeniably benefit from an in-depth fragment recognizer and candidate identifier.
-
-Tokens that are not part of a hand-annotated fragment, as well as single- or multi-token expressions from fragments, are simply looked up in the set of known anchors to determine their candidates.
-This works quite well for straightforward annotations like $Red\ Bull \rightarrow Red\_Bull$ (as it might appear in the AIDA data set), but is problematic with more obscure annotations like $Red\ Bull \rightarrow FC\_Red\_Bull\_Salzburg$ (as it might appear in the KORE50 data set).
-
-\subsection{Semantic signature vector for input}\label{subsection:semSigVector}
-To calculate the similarity score for each candidate, their semantic signature vector needs to compared to the semantic signature vector of the input.
-Unfortunately, the input does not have a semantic signature of its own.
-As a surrogate a candidate vector is generated as such: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$.
-For each candidate-entity of every fragment, check whether it already appears in the mapping.
-If not, add it to the map and set its count to one.
-If it exists, increment its count by one.
-
-Therefore a candidate's semantic signature similarity score increases as entities from their semantic signature appear more often as candidates in a given input (see Chapter \ref{subsec:VectorEvaluation} for the implementation).
-
-\subsection{tf--idf vector for input}\label{subsec:tfidfInput}
-The tf--idf vector for the input is calculated in the same fashion as for the candidates.
-The term frequency for every term in the input is found by counting all its occurrences, and its inverse document frequency is looked up in the idf map that was generated in Chapter \ref{sec:offlineTFIDF}.
-Terms that are unique to the input are ignored, as they do not affect the entity's vector score (they are multiplied by zero in the vector similarity calculation -- see Chapter \ref{sec:score computation}).
-
-\subsection{Score computation}\label{sec:score computation}
-The cosine similarity between the vectors $A$ and $B$ is calculated as follows
-$$\mathrm{similarity}(A, B) = \cos(\theta) = \frac{A \cdot B}{\|A\| \|B\|}$$
-
-There will be two similarity scores for each candidate:
-\begin{enumerate}
-\item The similarity $s_{\text{tf--idf}}$ between the tf--idf vectors of the input and the candidate.
-\item The similarity $s_{\text{semsig}}$ between the candidate vector of the input and the semantic signature vector of the candidate.
-\end{enumerate}
+See \cite{pageRank} for more information.
+This implementation uses the JUNG framework\footnote{Java Universal Network/Graph Framework: \url{http://jung.sourceforge.net/}} to calculate the page rank.
 
@@
 
-\begin{table}
-\centering
-\caption{Highest accuracy reached by {\acronym}, Babelfy, and DBpedia Spotlight.}
-\label{table:redirects}
-\begin{tabular}{ | c | c | c | c |}
-    \hline
-    & {\acronym} & Babelfy & DBpedia Spotlight \\ \hline
-    AIDA & x\% & 66.42\%* & 49.41\%\\ \hline
-    KORE50 & x\% & 47.89\% & x\%\\ \hline
-\end{tabular}
-\end{table}
+The systems under test were evaluated against a pre-annotated corpus for precision and recall. Precision, recall, and the derived $F_1$ score were defined as such:
+
+$$ precision = \frac{\text{\# of correctly assigned entities}}{\text{\# of all assigned entities}} $$
+
+$$ recall = \frac{\text{\# of correctly assigned entities}}{\text{\# of gold standard entities}} $$
+
+$$ F_1 = 2 \cdot \frac{precision \cdot recall}{precision + recall} $$
+
+\todo[inline]{Put up results}
+
 \section{Conclusion}\label{sec:conclusion}

### 2015-07-08 paper.tex
- added tables with preliminary results. - added a tiny paragraph to the introduction.

@@
 \usepackage{todonotes}
+%\usepackage{booktabs}
+\usepackage{tabularx}
+\newcolumntype{Y}{>{\centering\arraybackslash}X}
 
@@
 
-\todo[inline]{Write introduction}
+We evaluated V-SEL against the web services of FOX (Federated knOwledge eXtraction framework) and DBpedia Spotlight.
+FOX is a named entity recognition tool which uses AGDISTIS for entity linking.
+DBpedia Spotlight employs a four-staged approach which first recognizes and then links entities.
+
+\todo[inline]{Write introduction. Add references to bibliography.}
 
@@
 
+\begin{table}
+\centering
+\caption{Results for the AIDA-YAGO dataset.}
+\label{table:redirects}
+\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
+    \hline
+    & Fox & DBpedia spotlight & {\acronym}  \\ 
+    \hline
+    Precision  & 49.27\% & x\% & \textbf{59.33\%} \\
+    Recall & 29.68\% & x\% & \textbf{58.56\%} \\
+    $F_1$ & 0.37 & x &\textbf{0.59} \\
+    \hline
+\end{tabularx}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Results for the KORE50 dataset.}
+\label{table:redirects}
+\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
+    \hline
+    & Fox & DBpedia spotlight & {\acronym}  \\ 
+    \hline
+    Precision  & 30.0\% & x\% & 26.16\% \\
+    Recall & 20.83\% & x\% & 23.33\% \\
+    $F_1$ & 0.25 & x & 0.25 \\
+    \hline
+\end{tabularx}
+\end{table}
+
 \section{Conclusion}\label{sec:conclusion}

### 2015-07-08 paper.tex
- added some more results.
one polishing interation

--- 2015-07-07 paper.tex
@@
 %opening
-\title{Vector-Similarity based Entity Linking}
-\titlerunning{Vector-Similarity based Entity Linking}
+\title{Vector Similarity based Entity Linking}
+\titlerunning{Vector Similarity based Entity Linking}
 
@@
 \begin{abstract}
+\textbf{TODO}
 
-\keywords{Ontology lexicalization, DBpedia, \acronym{}}
+\keywords{Wikipedia, entity linking, vector similarity}
 \end{abstract}
@@
 \section{Introduction}\label{sec:introduction}
-Entity linking belongs to the field of natural language processing and is concerned with determining the identity of entities mentioned in a text.
-Note that entity linking is not concerned with recognizing a person as a person or a name as a name -- such a practice is the concern of a task known as named-entity recognition.
-Entity linking only refers to creating an association between a token in some form of input with the representation of an entity in some knowledge base.
 
-\todo[inline]{Write introduction}
+\emph{Entity linking} is the task of determining the identity of entities mentioned in a text.
+It usually follows a step of \emph{named entity recognition}, which identifies tokens that represent named entities and possibly classifies them w.r.t.
+predefined categories such as persons or locations.
+Entity linking therefore only refers to creating an association between a given token in textual input with the representation of an entity in some knowledge base.
+
+We present an approach to entity linking based on vector similarity (V-SEL), which can compete with existing state-of-the-art entity linking frameworks in terms of accuracy, and beats them significantly in terms of speed.
+In the following section we describe the approach, and then report evaluation results in Section~\ref{sec:results}.
 
 \section{Approach}\label{sec:approach}
-The input data for {\acronym} is a regular piece of text, for example a newspaper article (further referred to simply as \textit{input}), in which entity-representing fragments are already identified (possibly by named-entity recognition software).
-A \textit{fragment} from a given text is a token, or multiple successive tokens, which are representing the same entity.
-For a given fragment the algorithm is supposed to determine the matching real world entity.
-In order to do so, a set of entity \textit{candidates} for this fragment is needed, of which the algorithm has to pick the most likely correct one.
 
-A fragment which represents a real world entity is called an \textit{anchor}.
-To gather a database of anchors and their corresponding entities, data was extracted directly from a Wikipedia XML dump\footnote{More information on downloading Wikipedia dumps here: \url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}}.
-In these dumps a hyperlink to another page appears together like so:\\
-\centerline{\tt{[[Barack Obama|President Obama]]}}\\
-where {\textit{Barack Obama} refers to an entity\footnote{\url{http://en.wikipedia.org/wiki/Barack_Obama}} and \textit{President Obama} is the anchor string which appears in the page's text.
+The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (possibly by a named entity recognition tool).
+For a given fragment, the algorithm's task is to determine the matching real-world entity.
+It does so by picking the most likely entity from a set of entity candidates, e.g.
+specified in a knowledge base, in our case Wikipedia.
+
+A fragment which represents a real-world entity is called an \textit{anchor}.
+To gather a database of anchors and their corresponding entities, we extracted all anchor texts from a Wikipedia dump\footnote{\url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}}, in which hyperlinks to other pages appear in the form \texttt{[[Barack Obama|President Obama]]},
+where {\texttt{Barack Obama} refers to an entity\footnote{\url{http://en.wikipedia.org/wiki/Barack_Obama}} and \texttt{President Obama} is the anchor string which appears in the page's text.
 A map is generated by parsing all Wikipedia articles (in a chosen language) and counting the occurrences of anchor-entity pairs.
@@
 
-Candidates are scored by a support vector machine.
-\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four parameters are computed for each candidate, which are used as input for the SVM: tf--idf vector similarity, semantic signature vector similarity, candidate reference probability, and page rank.
+Candidates are scored by a support vector machine.\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four parameters are computed for each candidate, which are used as input for the SVM: tf-idf vector similarity, semantic signature vector similarity, candidate reference probability, and page rank.
+In the following we explain each of them in more detail.
 
@@
 \subsection{tf-idf Vector Similarity}
-The \textbf{tf--idf vector similarity} measures how similar the input is to the abstract of the candidate's Wikipedia entry with regards to the words which appear in both texts.
-The tf--idf value for a word reflects how important it is in a document, therefore if there is a large overlap between the important words in the input and the abstract of a candidate's Wikipedia page, the candidate is considered to be more likely correct.
-It calculated from the term frequency (tf) and inverse document frequency (idf).
-$\mathrm{tf}(t, d)$ is the raw frequency of term $t$ in document $d$.
-$\mathrm{idf}(t, D) $ is defines as such:
+
+The \textbf{tf-idf vector similarity} measures how similar the input is to the abstract of the candidate's Wikipedia entry with regards to the words which appear in both texts.
+The tf-idf value for a word reflects how important it is in a document, therefore if there is a large overlap between the important words in the input and the abstract of a candidate's Wikipedia page, the candidate is considered to be more likely correct.
+It is calculated based on the term frequency $\mathrm{tf}(t,d)$, defined as the raw frequency of term $t$ in document $d$, and the inverse document frequency $\mathrm{idf}(t,D)$, which is defines as follows:
 
@@
 
-where $N$ is the number of documents in the corpus and $|{d \in D : t \in d}|$ is the number of documents $t$ appears in. The tf-idf value is the product of the two:
+Where $N$ is the number of documents in the corpus and $|{d \in D : t \in d}|$ is the number of documents $t$ appears in. The tf-idf value is the product of the two:
 
@@
 
-The tf--idf vector $A$ for each entity is generated by picking the 100 (top 100 was an arbitrary choice to limit the maximal size of each datum) terms from its Wikipedia page's abstract $a$ with the highest tf--idf score.
-The tf value can be obtained by simply counting all occurrences of $t$ in $a$.
-The idf value can be obtained by treating the set of all entities' abstracts as the corpus and computing the idf score for every occurring word.
+V-SEL computes a tf-idf vector for each entity extracted from the Wikipedia dump by picking those 100 terms $t$ from the abstract $a$ of its Wikipedia page that have the highest tf-idf score.
+Here the tf-value can be obtained by simply counting all occurrences of $t$ in $a$, and the idf-value can be obtained by treating the set of all entity abstracts as the corpus and computing the idf-score for every occurring word.
 
-The tf--idf vector for the input $B$ is calculated in the same fashion as for the candidates.
-The term frequency for every term in the input is found by counting all its occurrences in the input text, and its inverse document frequency computed the same way as for each entity.
-Terms that are unique to the input are ignored, as they do not affect the entity's vector score (they are multiplied by zero in the vector similarity calculation).
+The tf-idf vector for the input is then computed in the same fashion, where the term frequency for every term in the input is determined by counting its occurrences in the input text.
+Terms that are unique in the input are ignored, as they do not affect the entity's vector score (they are multiplied by zero in the vector similarity calculation).
 
-The tf--idf vector similarity is then calculated as the cosine similarity between vectors $A$ and $B$:
+The tf-idf vector similarity is then calculated as the cosine similarity between two vectors $A$ (the input term) and $B$ (the candidate term):
 $$\mathrm{tfidfVectorSimilarity}(A, B) = \cos(\theta) = \frac{A \cdot B}{\|A\| \|B\|}$$
@@
 \subsection{Semantic Signature Vector Similarity}
-The \textbf{semantic signature vector similarity} measures the overlap between the candidate's \textbf{semantic signature} and the set of all candidates for the input.
-It stands to reason that a candidate is more likely to be the correct assignment for a given fragment if entities from its semantic signature are considered for other fragments (as related entities probably appear together).
 
-The semantic signature for an entity is computed as described in \cite{Babelfy}, but for the graph of interlinked Wikipedia pages (each page is a vertex, each link between pages is an edge) instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base.
+The \emph{semantic signature vector similarity} measures the overlap between the candidate's \emph{semantic signature} and the set of all candidates for the input.
+The rationale is that a candidate is more likely to be the correct assignment for a given fragment if entities from its semantic signature are considered for other fragments (as related entities probably appear together).
+
+The semantic signature for an entity is computed in the same ways as Babelfy \cite{Babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
 The idea is to identify for each page all other pages it is closely related to.
-This is a two step process:
-
-First, the edges will be assigned weights so that edges in denser parts of the graph become more important.
+This is a two step process.
+First, the edges are assigned weights so that edges in denser parts of the graph become more important.
 The weight of an edge $\mathrm{weight}(v, v')$ is the number of directed triangles (directed cycles of length 3) it appears in:
@@
 
-where $v$, $v'$ and $v''$ are vertices and $E$ is the set of all the graph's edges.
+Where $v$, $v'$ and $v''$ are vertices and $E$ is the set of all the graph's edges.
 
-Second, random walks with restart are performed from each vertex (a random walk is a path that consists of succession of random steps).
-For a number of $n$ steps\footnote{100.000 in this implementation.
-More would have not been computable in a reasonable time.} the graph is explored by `walking' to a connected vertex with probability $1 - \alpha$ or to move back to the vertex of origin with probability $\alpha$.
+Second, random walks with restart are performed from each vertex. % (a random walk is a path that consists of succession of random steps). 
+For a number of $n$ steps (in our case 100\,000, which are still computable within a reasonable timespan) the graph is explored by `walking' to a connected vertex with probability $1 - \alpha$ or to move back to the vertex of origin with probability $\alpha$.
 The probability of visiting the vertex $v'$ is based on the normalized weight of the connecting edge:
 $$P(v'|v) = \frac{\mathrm{weight}(v, v')}{\sum\limits_{v''\in V} \mathrm{weight}(v, v'')}$$
-where V is the set of all vertices in the graph.
+Where V is the set of all vertices in the graph.
 
@@
 The result is a frequency distribution of related vertices in which the vertices with the higher counts are interpreted as to be more relevant to the root vertex than vertices with lower counts.
-Vertices with a count lower than threshold $\tau$ are ignored\footnote{$\tau = 10$ for this implementation, so that $n$ and $\tau$ have the same ratio as in \cite{Babelfy}.}.
+Vertices with a count lower than threshold $\tau$ are ignored\footnote{$\tau = 10$ in our implementation, so that $n$ and $\tau$ have the same ratio as in Babelfy.}.
 
@@
 Unfortunately, the input does not have a semantic signature of its own.
-As a surrogate a candidate vector is generated as such: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$.
-For each candidate-entity of every fragment, check whether it already appears in the mapping.
+As a surrogate a candidate vector is generated as follows: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$.
+For each candidate entity of every fragment, check whether it already appears in the mapping.
 If not, add it to the map and set its count to one.
@@
 \subsection{Candidate Reference Probability}
-To account for how often an anchor refers to a given entity the \textbf{candidate reference probability} is incorporated into the score calculation.
-Using the word \textit{Michelangelo} as an anchor we might receive as candidates Michelangelo the Renaissance artist/engineer\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo}} and Michelangelo the Ninja Turtle\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo_(Teenage_Mutant_Ninja_Turtles)}}.
+
+To account for how often an anchor refers to a given entity, the \emph{candidate reference probability} is incorporated into the score calculation.
+For example, for the anchor \textit{Michelangelo} we might receive as candidates both the artist Michelangelo\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo}} and the Ninja Turtle Michelangelo\footnote{\url{http://en.wikipedia.org/wiki/Michelangelo_(Teenage_Mutant_Ninja_Turtles)}}.
 While both are valid candidates worthy of consideration, we can extract from Wikipedia that \textit{Michelangelo} referred only 21 times to the Ninja Turtle, but 1173 times to the artist.
@@
 
-where $\mathrm{ref}(a, e)$ is the number of references from anchor/candidate $a$ to entity $e$ and $E$ is the set of all anchors referring to $e$.
+Where $\mathrm{ref}(a, e)$ is the number of references from anchor/candidate $a$ to entity $e$ and $E$ is the set of all anchors referring to $e$.
 
@@
 \subsection{Page Rank}
-The idea behind the PageRank\cite{pageRank} algorithm was to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
-As Wikipedia entries form a highly interconnected graph the same principle can be applied to them to determine the page rank of an entity local to Wikipedia.
 
-Let $u$ be a web page. $B_u$ is the set of pages that have a hyperlink pointing to $u$. Let $N_u$ be the number of outgoing links for page $u$. A slightly simplified PageRank is then defined as such: 
+The idea behind the PageRank \cite{pageRank} algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
+As Wikipedia entries form a highly interconnected graph, the same principle can be applied in order to determine the page rank of an entity local to Wikipedia.
+
+Let $u$ be a web page.
+$B_u$ is the set of pages that have a hyperlink pointing to $u$.
+Let $N_u$ be the number of outgoing links for page $u$.
+A slightly simplified PageRank is then defined as follows:
 $$R(u) = c \sum_{v \in B_u} \frac{R(v)}{N_v}$$
-where $c$ is a normalizing factor.
+Where $c$ is a normalizing factor.
 Notably the PageRank of a page is derived from the PageRank of its incoming links, meaning that the algorithm has to be iterated until the system reaches a steady state.
-The overall PageRank for a graph is supposed to be constant, but there are corner cases (like cycles) that have to be accounted for.
-See \cite{pageRank} for more information.
-This implementation uses the JUNG framework\footnote{Java Universal Network/Graph Framework: \url{http://jung.sourceforge.net/}} to calculate the page rank.
+The overall PageRank for a graph is supposed to be constant, but there are corner cases (like cycles) that have to be accounted for; see \cite{pageRank} for more information.
+Our implementation uses the JUNG framework\footnote{Java Universal Network/Graph Framework: \url{http://jung.sourceforge.net/}}.
 
@@
 
-The systems under test were evaluated against a pre-annotated corpus for precision and recall. Precision, recall, and the derived $F_1$ score were defined as such:
+We evaluate our entity linking approach on two datasets, AIDA-YAGO and KOR50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}} \cite{spotlight},
+in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:
 
-$$ precision = \frac{\text{\# of correctly assigned entities}}{\text{\# of all assigned entities}} $$
+$$ Precision = \frac{\text{\# of correctly assigned entities}}{\text{\# of all assigned entities}} $$
 
-$$ recall = \frac{\text{\# of correctly assigned entities}}{\text{\# of gold standard entities}} $$
+$$ Recall = \frac{\text{\# of correctly assigned entities}}{\text{\# of gold standard entities}} $$
 
@@
 
-\todo[inline]{Put up results}
+Tables~\ref{table:redirects1} and~\ref{table:redirects2} shows the evaluation results. 
+\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA-YAGO dataset and achieves slightly worse but comparable results on the KOR50 dataset. 
+The latter is due to the fact that KORE50 was designed to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic signature vector overlaps.
+
+One of the biggest strengths of {\acronym} is its speed. 
+Running it on the full datasets took less than one minute for KORE50 and about 45 seconds for AIDA. 
+As comparison, running Bablfy on the KOR50 dataset takes about 15 minutes, and running it on AIDA had to be stopped after 164 hours.
+
+\begin{table}[t]
+\begin{center}
+\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
+    \hline
+    & FOX & DBpedia Spotlight & {\acronym}  \\ 
+    \hline
+    Precision  & 0.49 & 0.22 & \textbf{0.59} \\
+    Recall & 0.30 & 0.46 & \textbf{0.59} \\
+    $F_1$ & 0.37 & 0.30 & \textbf{0.59} \\
+    \hline
+\end{tabularx}
+\end{center}
+\caption{Results for the AIDA-YAGO dataset.}
+\label{table:redirects1}
+\end{table}
+
+\begin{table}[t]
+\begin{center}
+\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
+    \hline
+    & FOX & DBpedia Spotlight & {\acronym}  \\ 
+    \hline
+    Precision  & \textbf{0.30} & 0.22 & 0.26 \\
+    Recall & 0.21 & \textbf{0.34} & 0.23 \\
+    $F_1$ & 0.25 & \textbf{0.27} & 0.25 \\
+    \hline
+\end{tabularx}
+\end{center}
+\caption{Results for the KORE50 dataset.}
+\label{table:redirects2}
+\end{table}
+
+{\acronym} works best when a fragment refers to the most common meaning of a word.
+For example, assignments like \textit{BSE} $\rightarrow$ \texttt{Bovine\_spongiform\_encephalopathy} are usually correct.
+More ambiguous fragments get assigned correctly as well when that assignment is the most common one in the given context, for example \textit{commission} $\rightarrow$ \texttt{European\_Commission} in a debate of the European Parliament.
+Problems arise when the target entity is not the most common assignment for a given fragment.
+For example, the fragment \textit{Spanish} in \textit{Spanish Farm Minister Loyola de Palacio} leads to the assignment \textit{Spanish} $\rightarrow$ \texttt{Spanish\_Language}, as the fragment usually refers to the language, whereas the gold assignment is \textit{Spanish} $\rightarrow$ \texttt{Spain}.
+% This particular kind of case can be avoided by introducing syntactic information to the system, for example by using an automated part-of-speech tagger that can prevent the system of assigning a noun to an adjective fragment.
 
 \section{Conclusion}\label{sec:conclusion}
-The experiments have shown that {\acronym} is viable approach for entity linking.
-On the AIDA dataset, {\acronym} performs comparably to Babelfy and better than DBpedia Spotlight.
-On the KORE50 dataset however Babelfy reaches a higher accuracy than {\acronym}.
-KORE50 was built intentionally to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic signature vector overlaps.
 
-{\acronym} is very fast.
-Evaluating the full KORE50 dataset took about 15 minutes using the Babelfy algorithm, but less than one minute with {\acronym}.
-Evaluation of the AIDA dataset had to be stopped after 164 hours using the Babelfy algorithm.
-{\acronym} evaluates the same dataset in about 45 seconds.
-Since the entity identifier used in this approach tries to find candidates for every token in a text, the graphs used for the Babelfy evaluation become very large, which increases evaluation time.
-DBpedia Spotlight was not compared with respects to speed as it was not evaluated locally.
-
-{\acronym} works best when a fragment refers to the most common meaning of a word.
-For example, assignments like \textit{BSE $\rightarrow$ Bovine\_spongiform\_encephalopathy} or \textit{Franz Fischler $\rightarrow$ Franz\_Fischler} are usually correct.
-More ambiguous fragments get assigned correctly as well when that assignment is the most common one in the given context, for example \textit{commission $\rightarrow$ European\_Commission} in a debate of the European Parliament.
-Problems arise when the sought after entity is not the most common assignment for a given fragment.
-For example, the fragment \textit{Spanish} in \textit{Spanish Farm Minister Loyola de Palacio had earlier...} receives the assignment \textit{Spanish $\rightarrow$ Spanish\_Language}, as that token usually refers to the language.
-But the requested assignment was \textit{Spanish $\rightarrow$ Spain}.
-This particular kind of case can be avoided by introducing syntactic information to the system, for example by using an automated part of speech tagger.
-Using syntactic data would prevent the system of assigning a noun to an adjective-fragment.
+\textbf{TODO}
 

### 2015-07-09 paper.tex
added Christina

@@
 
-\author{Felix Tristram \and Sebastian Walter \and Philipp Cimiano}
-\authorrunning{Felix Tristram \and Sebastian Walter \and Philipp Cimiano}
+\author{Felix Tristram \and Christina Unger \and Sebastian Walter \and Philipp Cimiano}
+\authorrunning{Felix Tristram \and Christina Unger \and Sebastian Walter \and Philipp Cimiano}
 % (feature abused for this document to repeat the title also on left hand pages)

### 2015-07-09 paper.tex
committing changes

@@
 
-\newcommand{\acronym}{V-SEL}
+\newcommand{\acronym}{Veasel}
 
 %opening
-\title{Vector Similarity based Entity Linking}
-\titlerunning{Vector Similarity based Entity Linking}
+\title{Veasel meets Fox: an ensemble approach to entity linking based on vector similarity }
+\titlerunning{Veasel meets Fox}
 
@@
 \begin{abstract}
-\textbf{TODO}
+The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
+We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is induced using a Support Vector Machine.
+We compare our approach to state-of-the-art tools such as Fox and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
+An important feature of Veasel is its speed.
 
@@
 
-\emph{Entity linking} is the task of determining the identity of entities mentioned in a text.
-It usually follows a step of \emph{named entity recognition}, which identifies tokens that represent named entities and possibly classifies them w.r.t.
-predefined categories such as persons or locations.
-Entity linking therefore only refers to creating an association between a given token in textual input with the representation of an entity in some knowledge base.
+The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
+We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is induced using a Support Vector Machine.
+Given a named entity and a resource candidate, Veasel combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measures as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
+An optimal linear model is trained using an SVM to induce an ensemble that combines these four features into an overall decision whether the named entity refers to a candidate resources or not.
 
-We present an approach to entity linking based on vector similarity (V-SEL), which can compete with existing state-of-the-art entity linking frameworks in terms of accuracy, and beats them significantly in terms of speed.
+As underlying knowledge base, we use DBpedia and rely on Wikipedia pages as textual context of the resources in DBpedia to extract our textual features.
+
+We compare our approach to state-of-the-art tools such as Fox and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
+Further, we show that Veasel beets state-of-the-art named entity linking approaches in terms of speed.
+
 In the following section we describe the approach, and then report evaluation results in Section~\ref{sec:results}.
@@
 
-Candidates are scored by a support vector machine.\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four parameters are computed for each candidate, which are used as input for the SVM: tf-idf vector similarity, semantic signature vector similarity, candidate reference probability, and page rank.
+Candidates are scored by a support vector machine.\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four features are computed for each candidate, which are used as input for the SVM: tf-idf vector similarity, semantic signature vector similarity, candidate reference probability, and page rank.
 In the following we explain each of them in more detail.
@@
 The tf-idf value for a word reflects how important it is in a document, therefore if there is a large overlap between the important words in the input and the abstract of a candidate's Wikipedia page, the candidate is considered to be more likely correct.
-It is calculated based on the term frequency $\mathrm{tf}(t,d)$, defined as the raw frequency of term $t$ in document $d$, and the inverse document frequency $\mathrm{idf}(t,D)$, which is defines as follows:
+It is calculated based on the term frequency $\mathrm{tf}(t,d)$, defined as the raw frequency of term $t$ in document $d$, and the inverse document frequency $\mathrm{idf}(t,D)$, which is defined as follows:
 
@@
 
-V-SEL computes a tf-idf vector for each entity extracted from the Wikipedia dump by picking those 100 terms $t$ from the abstract $a$ of its Wikipedia page that have the highest tf-idf score.
+Veasel computes a tf-idf vector for each entity extracted from the Wikipedia dump by picking those 100 terms $t$ from the abstract $a$ of its Wikipedia page that have the highest tf-idf score.
 Here the tf-value can be obtained by simply counting all occurrences of $t$ in $a$, and the idf-value can be obtained by treating the set of all entity abstracts as the corpus and computing the idf-score for every occurring word.
@@
 
-The semantic signature for an entity is computed in the same ways as Babelfy \cite{Babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
-The idea is to identify for each page all other pages it is closely related to.
+The semantic neighborhood signature for an entity is computed in the same ways as Babelfy \cite{Babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
+The idea is to identify for each resource all other resources it is closely related to.
 This is a two step process.
@@
 
+Overall, by the above we thus compute in essence a measure similar to the \emph{personalized page rank} \cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy \cite{}.
+This step is performed offline.
+
 To calculate the similarity score for each candidate, their semantic signature vector needs to compared to the semantic signature vector of the input.
@@
 Therefore a candidate's semantic signature similarity score increases as entities from their semantic signature appear more often as candidates in a given input.
+The top 10 elements in the semantic neighborhood signature of Barack Obama are for instance:
 
@@
 The idea behind the PageRank \cite{pageRank} algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
-As Wikipedia entries form a highly interconnected graph, the same principle can be applied in order to determine the page rank of an entity local to Wikipedia.
+As DBpedia entries form a highly interconnected graph, the same principle can be applied in order to determine the page rank of a resource in DBpedia.
 
@@
 
-$$ Precision = \frac{\text{\# of correctly assigned entities}}{\text{\# of all assigned entities}} $$
+$$Precision = \frac{\text{\# of correctly assigned entities}}{\text{\# of all assigned entities}}$$
 
-$$ Recall = \frac{\text{\# of correctly assigned entities}}{\text{\# of gold standard entities}} $$
+$$Recall = \frac{\text{\# of correctly assigned entities}}{\text{\# of gold standard entities}}$$
 
-$$ F_1 = 2 \cdot \frac{precision \cdot recall}{precision + recall} $$
+$$F_1 = 2 \cdot \frac{precision \cdot recall}{precision + recall}$$
+
+Precision, Recall and F-Measure are micro-averaged over all named entities. Documents in which more named entities occur have thus a larger impact on the scores.
 
@@
 Running it on the full datasets took less than one minute for KORE50 and about 45 seconds for AIDA. 
-As comparison, running Bablfy on the KOR50 dataset takes about 15 minutes, and running it on AIDA had to be stopped after 164 hours.
+As comparison, running Babelfy on the KOR50 dataset takes about 15 minutes, and running it on AIDA had to be stopped after 164 hours.
 
@@
 
-\textbf{TODO}
+We have presented Veasel, a new entity linking approach that exploits an ensemble of features that are linearly combined using a Support Vector Machine.
+We have shown that the approach works very will when the contexts are longer, clearly outperforming Fox and DBpedia Spotlight on the AIDA CoNLL dataset.
+On the KORE50 dataset where contexts are shorter, it achieves comparable results to these approaches.
+In future work, we will release a service that can be publicly accessed using a similar interface to DBpedia Spotlight and Fox.
+We will also extend the approach to other languages and perform a more systematic evaluation using the GERBIL framework \cite{gebril}.
+
+%Ricardo Usbeck, Michael Röder, Axel-Cyrille Ngonga Ngomo, Ciro Baron, Andreas Both, Martin Brümmer, Diego Ceccarelli, Marco Cornolti, Didier Cherix, Bernd Eickmann, Paolo Ferragina, Christiane Lemke, Andrea Moro, Roberto Navigli, Francesco Piccinno, Giuseppe Rizzo, Harald Sack, René Speck, Raphaël Troncy, Jörg Waitelonis, Lars Wesemann:
+%GERBIL: General Entity Annotator Benchmarking Framework. WWW 2015: 1133-1143
 

### 2015-07-09 paper.tex
- some spelling/grammar fixes - merged the result tables - added some bibliography stuff - changed semantic signature to semantic neighborhood signature

@@
 \usepackage{todonotes}
-%\usepackage{booktabs}
+\usepackage{booktabs}
 \usepackage{tabularx}
@@
 We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is induced using a Support Vector Machine.
-Given a named entity and a resource candidate, Veasel combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measures as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
+Given a named entity and a resource candidate, Veasel combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measures as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood signature of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
 An optimal linear model is trained using an SVM to induce an ensemble that combines these four features into an overall decision whether the named entity refers to a candidate resources or not.
@@
 We compare our approach to state-of-the-art tools such as Fox and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
-Further, we show that Veasel beets state-of-the-art named entity linking approaches in terms of speed.
+Further, we show that Veasel beats state-of-the-art named entity linking approaches in terms of speed.
 
@@
 A fragment which represents a real-world entity is called an \textit{anchor}.
-To gather a database of anchors and their corresponding entities, we extracted all anchor texts from a Wikipedia dump\footnote{\url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}}, in which hyperlinks to other pages appear in the form \texttt{[[Barack Obama|President Obama]]},
+To gather a database of anchors and their corresponding entities, we extracted all anchor texts from a Wikipedia dump\footnote{\url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}}.
+Within a dump hyperlinks to other pages appear in the form \texttt{[[Barack Obama|President Obama]]},
 where {\texttt{Barack Obama} refers to an entity\footnote{\url{http://en.wikipedia.org/wiki/Barack_Obama}} and \texttt{President Obama} is the anchor string which appears in the page's text.
@@
 
-Candidates are scored by a support vector machine.\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four features are computed for each candidate, which are used as input for the SVM: tf-idf vector similarity, semantic signature vector similarity, candidate reference probability, and page rank.
+Candidates are scored by a support vector machine.\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four features are computed for each candidate, which are used as input for the SVM: tf-idf vector similarity, semantic neighborhood signature vector similarity, candidate reference probability, and page rank.
 In the following we explain each of them in more detail.
@@
 
-The tf-idf vector similarity is then calculated as the cosine similarity between two vectors $A$ (the input term) and $B$ (the candidate term):
+The tf-idf vector similarity is then calculated as the cosine similarity between two vectors $A$ (the input terms) and $B$ (the candidate terms):
 $$\mathrm{tfidfVectorSimilarity}(A, B) = \cos(\theta) = \frac{A \cdot B}{\|A\| \|B\|}$$
@@
 % ------------ semantic signature vector similarity -------------------
-\subsection{Semantic Signature Vector Similarity}
+\subsection{Semantic Neighborhood Signature Vector Similarity}
 
-The \emph{semantic signature vector similarity} measures the overlap between the candidate's \emph{semantic signature} and the set of all candidates for the input.
-The rationale is that a candidate is more likely to be the correct assignment for a given fragment if entities from its semantic signature are considered for other fragments (as related entities probably appear together).
+The \emph{semantic neighborhood signature vector similarity} measures the overlap between the candidate's \emph{semantic neighborhood signature} and the set of all candidates for the input.
+The rationale is that a candidate is more likely to be the correct assignment for a given fragment if entities from its semantic neighborhood signature are considered for other fragments (as related entities probably appear together).
 
-The semantic neighborhood signature for an entity is computed in the same ways as Babelfy \cite{Babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
+The semantic neighborhood signature for an entity is computed in the same ways as Babelfy \cite{babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
 The idea is to identify for each resource all other resources it is closely related to.
@@
 During the random walk for a given root vertex $v_r$, the visits to each vertex $v_i (i \neq r)$ are counted.
-The result is a frequency distribution of related vertices in which the vertices with the higher counts are interpreted as to be more relevant to the root vertex than vertices with lower counts.
+The result is a frequency distribution of related vertices in which the vertices with higher counts are interpreted as to be more relevant to the root vertex than vertices with lower counts.
 Vertices with a count lower than threshold $\tau$ are ignored\footnote{$\tau = 10$ in our implementation, so that $n$ and $\tau$ have the same ratio as in Babelfy.}.
 
-Overall, by the above we thus compute in essence a measure similar to the \emph{personalized page rank} \cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy \cite{}.
+In its essence we thus compute a measure similar to the \emph{personalized page rank} \cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy.
 This step is performed offline.
 
-To calculate the similarity score for each candidate, their semantic signature vector needs to compared to the semantic signature vector of the input.
-Unfortunately, the input does not have a semantic signature of its own.
+To calculate the similarity score for each candidate, their semantic neighborhood signature vector needs to compared to the semantic neighborhood signature vector of the input.
+Unfortunately, the input does not have a semantic neighborhood signature of its own.
 As a surrogate a candidate vector is generated as follows: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$.
@@
 
-Therefore a candidate's semantic signature similarity score increases as entities from their semantic signature appear more often as candidates in a given input.
+Therefore a candidate's semantic neighborhood signature similarity score increases as entities from their semantic neighborhood signature appear more often as candidates in a given input.
 The top 10 elements in the semantic neighborhood signature of Barack Obama are for instance:
+\begin{enumerate}
+\item United\_States\_House\_of\_Representatives\_elections,\_2010
+\item Barack\_Obama
+\item Presidency\_of\_Barack\_Obama
+\item United\_States\_presidential\_election,\_2008
+\item Barack\_Obama\_presidential\_primary\_campaign,\_2008
+\item First\_inauguration\_of\_Barack\_Obama
+\item Democratic\_Party\_(United\_States)
+\item George\_W.\_Bush
+\item Republican\_Party\_(United\_States)
+\item Joe\_Biden
+\end{enumerate}
 
@@
 
-We evaluate our entity linking approach on two datasets, AIDA-YAGO and KOR50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}} \cite{spotlight},
+We evaluate our entity linking approach on two datasets, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}} \cite{spotlight},
 in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:
@@
 
-Tables~\ref{table:redirects1} and~\ref{table:redirects2} shows the evaluation results. 
-\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA-YAGO dataset and achieves slightly worse but comparable results on the KOR50 dataset. 
-The latter is due to the fact that KORE50 was designed to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic signature vector overlaps.
+Table~\ref{table:redirects1} shows the evaluation results. 
+\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA-YAGO dataset and achieves slightly worse but comparable results on the KORE50 dataset. 
+The latter is due to the fact that KORE50 was designed to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic neighborhood signature vector overlaps.
 
@@
 Running it on the full datasets took less than one minute for KORE50 and about 45 seconds for AIDA.
-As comparison, running Babelfy on the KOR50 dataset takes about 15 minutes, and running it on AIDA had to be stopped after 164 hours.
+\todo[inline]{Redo measurements with the latest approach.}
+%As comparison, running Babelfy on the KORE50 dataset takes about 15 minutes, and running it on AIDA had to be stopped after 164 hours.
 
@@
 \begin{center}
-\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
-    \hline
-    & FOX & DBpedia Spotlight & {\acronym}  \\ 
-    \hline
-    Precision  & 0.49 & 0.22 & \textbf{0.59} \\
-    Recall & 0.30 & 0.46 & \textbf{0.59} \\
-    $F_1$ & 0.37 & 0.30 & \textbf{0.59} \\
-    \hline
+\begin{tabularx}{\textwidth}{ c Y Y Y Y Y Y}
+\toprule
+& \multicolumn{3}{c}{AIDA/CoNLL}  
+& \multicolumn{3}{c}{KORE50}\\
+\cmidrule(lr){2-4} \cmidrule(lr){5-7}
+& Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ 
+\midrule
+FOX & 0.49 & 0.30 & 0.37 & \textbf{0.30} & 0.21 &  0.25 \\
+DBpedia Spotlight & 0.22 & 0.46 & 0.30 & 0.22 & \textbf{0.34} & \textbf{0.27} \\
+{\acronym} & \textbf{0.59} & \textbf{0.59} & \textbf{0.59} & 0.26 & 0.23 &  0.25 \\
+\bottomrule
 \end{tabularx}
 \end{center}
-\caption{Results for the AIDA-YAGO dataset.}
+\caption{Results for the AIDA/CoNLL and KORE50 datasets.}
 \label{table:redirects1}
-\end{table}
-
-\begin{table}[t]
-\begin{center}
-\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
-    \hline
-    & FOX & DBpedia Spotlight & {\acronym}  \\ 
-    \hline
-    Precision  & \textbf{0.30} & 0.22 & 0.26 \\
-    Recall & 0.21 & \textbf{0.34} & 0.23 \\
-    $F_1$ & 0.25 & \textbf{0.27} & 0.25 \\
-    \hline
-\end{tabularx}
-\end{center}
-\caption{Results for the KORE50 dataset.}
-\label{table:redirects2}
 \end{table}
@@
 We have presented Veasel, a new entity linking approach that exploits an ensemble of features that are linearly combined using a Support Vector Machine.
-We have shown that the approach works very will when the contexts are longer, clearly outperforming Fox and DBpedia Spotlight on the AIDA CoNLL dataset.
+We have shown that the approach works very well when the contexts are longer, clearly outperforming Fox and DBpedia Spotlight on the AIDA CoNLL dataset.
 On the KORE50 dataset where contexts are shorter, it achieves comparable results to these approaches.
 In future work, we will release a service that can be publicly accessed using a similar interface to DBpedia Spotlight and Fox.
-We will also extend the approach to other languages and perform a more systematic evaluation using the GERBIL framework \cite{gebril}.
+We will also extend the approach to other languages and perform a more systematic evaluation using the GERBIL framework \cite{gerbil}.
 

### 2015-07-10 paper.tex
minor changes

@@
 %opening
-\title{Veasel meets Fox: an ensemble approach to entity linking based on vector similarity }
-\titlerunning{Veasel meets Fox}
+\title{Veasel meets FOX: an ensemble approach to entity linking based on vector similarity }
+\titlerunning{Veasel meets FOX}
 
-\author{Felix Tristram \and Christina Unger \and Sebastian Walter \and Philipp Cimiano}
-\authorrunning{Felix Tristram \and Christina Unger \and Sebastian Walter \and Philipp Cimiano}
+\author{Felix Tristram \and Sebastian Walter \and Philipp Cimiano  \and Christina Unger}
+\authorrunning{Felix Tristram \and Sebastian Walter \and Philipp Cimiano  \and Christina Unger}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
-We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is induced using a Support Vector Machine.
-We compare our approach to state-of-the-art tools such as Fox and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
+We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
+We compare our approach to state-of-the-art tools such as FOX and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
 An important feature of Veasel is its speed.
@@
 The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
-We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is induced using a Support Vector Machine.
-Given a named entity and a resource candidate, Veasel combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measures as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood signature of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
-An optimal linear model is trained using an SVM to induce an ensemble that combines these four features into an overall decision whether the named entity refers to a candidate resources or not.
+We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
+Given a named entity and a resource candidate, Veasel combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measured as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood signature of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
+An optimal linear model is trained using an SVM to induce an ensemble that combines these four features into an overall decision whether the named entity refers to a candidate resource or not.
 
@@
 
-We compare our approach to state-of-the-art tools such as Fox and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
+We compare our approach to state-of-the-art tools such as FOX\cite{foxdemo} and DBpedia spotlight\cite{spotlight}, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
 Further, we show that Veasel beats state-of-the-art named entity linking approaches in terms of speed.
 
-In the following section we describe the approach, and then report evaluation results in Section~\ref{sec:results}.
+In the following section we describe the approach and then report evaluation results in Section~\ref{sec:results}.
 
@@
 
-The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (possibly by a named entity recognition tool).
+The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (we use the Stanford NER \cite{ner}).
 For a given fragment, the algorithm's task is to determine the matching real-world entity.
 It does so by picking the most likely entity from a set of entity candidates, e.g.
-specified in a knowledge base, in our case Wikipedia.
+specified in a knowledge base, in our case DBpedia.
 
@@
 To gather a database of anchors and their corresponding entities, we extracted all anchor texts from a Wikipedia dump\footnote{\url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}}.
-Within a dump hyperlinks to other pages appear in the form \texttt{[[Barack Obama|President Obama]]},
+Within a dump, hyperlinks to other pages appear in the form \texttt{[[Barack Obama|President Obama]]},
 where {\texttt{Barack Obama} refers to an entity\footnote{\url{http://en.wikipedia.org/wiki/Barack_Obama}} and \texttt{President Obama} is the anchor string which appears in the page's text.
 A map is generated by parsing all Wikipedia articles (in a chosen language) and counting the occurrences of anchor-entity pairs.
-The candidates for a given fragment are now found by looking up all entities that were referred to by the fragment within Wikipedia.
+The candidates for a given fragment are found by looking up all entities that were referred to by the fragment within Wikipedia.
 
@@
 
-The semantic neighborhood signature for an entity is computed in the same ways as Babelfy \cite{babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
+The semantic neighborhood signature for an entity is computed in a similar way as Babelfy \cite{babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
 The idea is to identify for each resource all other resources it is closely related to.
@@
 
-In its essence we thus compute a measure similar to the \emph{personalized page rank} \cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy.
-This step is performed offline.
+We compute a measure similar to the \emph{personalized page rank} \cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy. This step is performed offline.
 
@@
 Therefore a candidate's semantic neighborhood signature similarity score increases as entities from their semantic neighborhood signature appear more often as candidates in a given input.
-The top 10 elements in the semantic neighborhood signature of Barack Obama are for instance:
-\begin{enumerate}
-\item United\_States\_House\_of\_Representatives\_elections,\_2010
-\item Barack\_Obama
-\item Presidency\_of\_Barack\_Obama
-\item United\_States\_presidential\_election,\_2008
-\item Barack\_Obama\_presidential\_primary\_campaign,\_2008
-\item First\_inauguration\_of\_Barack\_Obama
-\item Democratic\_Party\_(United\_States)
-\item George\_W.\_Bush
-\item Republican\_Party\_(United\_States)
-\item Joe\_Biden
-\end{enumerate}
+%The top 10 elements in the semantic neighborhood signature of Barack Obama are for instance:
+%\begin{enumerate}
+%\item United\_States\_House\_of\_Representatives\_elections,\_2010
+%\item Barack\_Obama
+%\item Presidency\_of\_Barack\_Obama
+%\item United\_States\_presidential\_election,\_2008
+%\item Barack\_Obama\_presidential\_primary\_campaign,\_2008
+%\item First\_inauguration\_of\_Barack\_Obama
+%\item Democratic\_Party\_(United\_States)
+%\item George\_W.\_Bush
+%\item Republican\_Party\_(United\_States)
+%\item Joe\_Biden
+%\end{enumerate}
 
@@
 Running it on the full datasets took less than one minute for KORE50 and about 45 seconds for AIDA.
-\todo[inline]{Redo measurements with the latest approach.}
+%\todo[inline]{Redo measurements with the latest approach.}
 %As comparison, running Babelfy on the KORE50 dataset takes about 15 minutes, and running it on AIDA had to be stopped after 164 hours.
@@
 We have presented Veasel, a new entity linking approach that exploits an ensemble of features that are linearly combined using a Support Vector Machine.
-We have shown that the approach works very well when the contexts are longer, clearly outperforming Fox and DBpedia Spotlight on the AIDA CoNLL dataset.
+We have shown that the approach works very well when the contexts are longer, clearly outperforming FOX and DBpedia Spotlight on the AIDA CoNLL dataset.
 On the KORE50 dataset where contexts are shorter, it achieves comparable results to these approaches.
-In future work, we will release a service that can be publicly accessed using a similar interface to DBpedia Spotlight and Fox.
+In future work, we will release a service that can be publicly accessed using a similar interface to DBpedia Spotlight and FOX.
 We will also extend the approach to other languages and perform a more systematic evaluation using the GERBIL framework \cite{gerbil}.

### 2015-07-10 paper.tex
minor updates

@@
 
-We compare our approach to state-of-the-art tools such as FOX\cite{foxdemo} and DBpedia spotlight\cite{spotlight}, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
+We compare our approach to state-of-the-art tools such as FOX~\cite{foxdemo} and DBpedia spotlight~\cite{spotlight}, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
 Further, we show that Veasel beats state-of-the-art named entity linking approaches in terms of speed.
@@
 
-The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (we use the Stanford NER \cite{ner}).
+The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (we use the Stanford NER~\cite{ner}).
 For a given fragment, the algorithm's task is to determine the matching real-world entity.
@@
 
-The semantic neighborhood signature for an entity is computed in a similar way as Babelfy \cite{babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
+The semantic neighborhood signature for an entity is computed in a similar way as Babelfy~\cite{babelfy} does, except that instead of the BabelNet\footnote{\url{http://babelnet.org/}} knowledge base we use a graph of interlinked Wikipedia pages, where each page is a vertex and each link between pages is an edge.
 The idea is to identify for each resource all other resources it is closely related to.
@@
 
-We compute a measure similar to the \emph{personalized page rank} \cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy. This step is performed offline.
+We compute a measure similar to the \emph{personalized page rank}~\cite{personalized_page_rank} using a random walk approach similar to the one implemented in Babelfy. This step is performed offline.
 
@@
 
-The idea behind the PageRank \cite{pageRank} algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
+The idea behind the PageRank~\cite{pageRank} algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
 As DBpedia entries form a highly interconnected graph, the same principle can be applied in order to determine the page rank of a resource in DBpedia.

### 2015-07-10 paper.tex
minor update

@@
 
-We evaluate our entity linking approach on two datasets, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}} \cite{spotlight},
+We evaluate our entity linking approach on two datasets, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},
 in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:

### 2015-08-19 paper.tex
added Acknowledgment
- replaced all hard-coded names with \acronym macros - renamed Veasel to Weasel - removed claims of high speed

@@
 
-\newcommand{\acronym}{Veasel}
+\newcommand{\acronym}{Weasel}
 
 %opening
-\title{Veasel meets FOX: an ensemble approach to entity linking based on vector similarity }
-\titlerunning{Veasel meets FOX}
+\title{{\acronym} meets FOX: an ensemble approach to entity linking based on vector similarity }
+\titlerunning{{\acronym} meets FOX}
 
@@
 The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
-We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
+We present \emph{{\acronym}}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
 We compare our approach to state-of-the-art tools such as FOX and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
-An important feature of Veasel is its speed.
 
@@
 The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
-We present \emph{Veasel}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
-Given a named entity and a resource candidate, Veasel combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measured as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood signature of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
+We present \emph{{\acronym}}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
+Given a named entity and a resource candidate, {\acronym} combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measured as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood signature of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
 An optimal linear model is trained using an SVM to induce an ensemble that combines these four features into an overall decision whether the named entity refers to a candidate resource or not.
@@
 We compare our approach to state-of-the-art tools such as FOX~\cite{foxdemo} and DBpedia spotlight~\cite{spotlight}, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
-Further, we show that Veasel beats state-of-the-art named entity linking approaches in terms of speed.
 
@@
 
-Veasel computes a tf-idf vector for each entity extracted from the Wikipedia dump by picking those 100 terms $t$ from the abstract $a$ of its Wikipedia page that have the highest tf-idf score.
+{\acronym} computes a tf-idf vector for each entity extracted from the Wikipedia dump by picking those 100 terms $t$ from the abstract $a$ of its Wikipedia page that have the highest tf-idf score.
 Here the tf-value can be obtained by simply counting all occurrences of $t$ in $a$, and the idf-value can be obtained by treating the set of all entity abstracts as the corpus and computing the idf-score for every occurring word.
@@
 
-One of the biggest strengths of {\acronym} is its speed. 
-Running it on the full datasets took less than one minute for KORE50 and about 45 seconds for AIDA.
-%\todo[inline]{Redo measurements with the latest approach.}
-%As comparison, running Babelfy on the KORE50 dataset takes about 15 minutes, and running it on AIDA had to be stopped after 164 hours.
-
 \begin{table}[t]
@@
 
-We have presented Veasel, a new entity linking approach that exploits an ensemble of features that are linearly combined using a Support Vector Machine.
+We have presented {\acronym}, a new entity linking approach that exploits an ensemble of features that are linearly combined using a Support Vector Machine.
 We have shown that the approach works very well when the contexts are longer, clearly outperforming FOX and DBpedia Spotlight on the AIDA CoNLL dataset.
@@
 
+\section*{Acknowledgment}
+This work was supported by the Cluster of Excellence Cognitive Interaction Technology \emph{CITEC} (EXC 277) at Bielefeld University, which is funded by the German Research Foundation (DFG).
+
 \bibliographystyle{plain}

### 2015-08-20 paper.tex
- added upper bound values for precision and recall for both datasets

@@
 
+The quality of the NER used to find entities poses an upper bound on the achievable entity linking scores.
+For the AIDA/CoNLL dataset the highest achievable linking precision is 0.79, while the highest achievable recall is 0.98 (max.
+$F_1$: 0.88).
+For the KORE50 dataset the values are 0.93 and 0.88 respectively (max.
+$F_1$: 0.90).
+
 Table~\ref{table:redirects1} shows the evaluation results. 
-\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA-YAGO dataset and achieves slightly worse but comparable results on the KORE50 dataset. 
+\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA/CoNLL dataset and achieves slightly worse but comparable results on the KORE50 dataset. 
 The latter is due to the fact that KORE50 was designed to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic neighborhood signature vector overlaps.

### 2015-08-20 paper.tex
- added a footnote with the url for the result download

@@
 
-We evaluate our entity linking approach on two datasets, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},
+We evaluate our entity linking approach on two datasets\footnote{{\acronym}'s results for the 10-fold cross validations can be downloaded from: \url{http://sebastianwalter.org/weasel/nFoldresults.zip}}, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},
 in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:

### 2015-08-20 paper.tex
- replaced "ensemble" with "combination"

@@
 %opening
-\title{{\acronym} meets FOX: an ensemble approach to entity linking based on vector similarity }
+\title{{\acronym} meets FOX: a combined approach to entity linking based on vector similarity }
 \titlerunning{{\acronym} meets FOX}
@@
 The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
-We present \emph{{\acronym}}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
+We present \emph{{\acronym}}, a novel approach that is based on a combination of different features that is trained using a Support Vector Machine.
 We compare our approach to state-of-the-art tools such as FOX and DBpedia spotlight, showing that it outperforms both on the AIDA/CoNLL dataset and provides comparable results on the KORE50 dataset.
@@
 The task of entity linking consists in disambiguating named entities occurring in textual data by linking them to an identifier in a knowledge base that represents the real-world entity they denote.
-We present \emph{{\acronym}}, a novel approach that is based on an ensemble of different features that is trained using a Support Vector Machine.
+We present \emph{{\acronym}}, a novel approach that is based on a combination of different features that is trained using a Support Vector Machine.
 Given a named entity and a resource candidate, {\acronym} combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measured as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood signature of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
-An optimal linear model is trained using an SVM to induce an ensemble that combines these four features into an overall decision whether the named entity refers to a candidate resource or not.
+An optimal non-linear model is trained using an SVM which combines these four features into an overall decision whether the named entity refers to a candidate resource or not.
 
@@
 
-We have presented {\acronym}, a new entity linking approach that exploits an ensemble of features that are linearly combined using a Support Vector Machine.
+We have presented {\acronym}, a new entity linking approach that exploits a combination of features that are linearly combined using a Support Vector Machine.
 We have shown that the approach works very well when the contexts are longer, clearly outperforming FOX and DBpedia Spotlight on the AIDA CoNLL dataset.

### 2015-08-20 paper.tex
- added a table for the results with reduced component sets. Still waiting on some results to fill in some data points.

@@
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
+\newcolumntype{s}{>{\hsize=2\hsize}X}
 
@@
 
+\begin{table}[t]
+\begin{center}
+\begin{tabularx}{\textwidth}{ X Y Y Y Y Y Y}
+\toprule
+& \multicolumn{3}{c}{AIDA/CoNLL}  
+& \multicolumn{3}{c}{KORE50}\\
+\cmidrule(lr){2-4} \cmidrule(lr){5-7}
+ & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ 
+\midrule
+\emph{without} &  &  &  &  &  &  \\ 
+SNS & x & x & x & 0.32 & 0.28 &  0.29 \\
+tf-idf & x & x & x & 0.32 & 0.28 &  0.29 \\
+page rank & x & x & x & 0.12 & 0.10 &  0.11 \\
+CRP & x & x & x & 0.31 & 0.27 & 0.29 \\
+\midrule
+\emph{only with} &  &  &  &  &  &  \\ 
+SNS & x & x & x & 0.07 & 0.06 &  0.06 \\
+tf-idf & x & x & x & 0.08 & 0.07 &  0.07 \\
+page rank & x & x & x & 0.32 & 0.28 &  0.29 \\
+CRP & x & x & x & 0.08 & 0.07 &  0.07 \\
+\bottomrule
+\end{tabularx}
+\end{center}
+\caption{Results for the AIDA/CoNLL and KORE50 datasets when one of the components is removed and when only one component is used for classification.
+SNS is Semantic Neighborhood Signature Vector Similarity, CRP is Candidate Reference Probability.}
+\label{table:components}
+\end{table}
+
 \section{Conclusion}\label{sec:conclusion}

### 2015-08-20 paper.tex
- added second download link for results

@@
 
-We evaluate our entity linking approach on two datasets\footnote{{\acronym}'s results for the 10-fold cross validations can be downloaded from: \url{http://sebastianwalter.org/weasel/nFoldresults.zip}}, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},
+We evaluate our entity linking approach on two datasets\footnote{{\acronym}'s results for the 10-fold cross validations can be downloaded from: \url{http://sebastianwalter.org/weasel/nFoldResultsAIDA.zip} and \url{http://sebastianwalter.org/weasel/nFoldResultsKore50.zip}}, AIDA/CoNLL and KORE50, and compare its results with two other state-of-the-art entity linking approaches, AGDISTIS \cite{agdistis} as part of FOX\footnote{\url{http://aksw.org/Projects/FOX.html}}, and DBpedia Spotlight\footnote{\url{http://spotlight.dbpedia.org}},
 in terms of precision and recall. Precision, recall, and the derived $F_1$ score were defined as follows:
@@
 FOX & 0.49 & 0.30 & 0.37 & \textbf{0.30} & 0.21 &  0.25 \\
-DBpedia Spotlight & 0.22 & 0.46 & 0.30 & 0.22 & \textbf{0.34} & \textbf{0.27} \\
-{\acronym} & \textbf{0.59} & \textbf{0.59} & \textbf{0.59} & 0.26 & 0.23 &  0.25 \\
+DBpedia Spotlight & 0.22 & 0.46 & 0.30 & 0.22 & \textbf{0.34} & 0.27 \\
+{\acronym} & \textbf{0.60} & \textbf{0.57} & \textbf{0.58} & \textbf{0.30} & 0.26 &  \textbf{0.28} \\
 \bottomrule

### 2015-08-21 paper.tex
- added second half of table

@@
 \emph{without} &  &  &  &  &  &  \\ 
-SNS & x & x & x & 0.32 & 0.28 &  0.29 \\
-tf-idf & x & x & x & 0.32 & 0.28 &  0.29 \\
-page rank & x & x & x & 0.12 & 0.10 &  0.11 \\
-CRP & x & x & x & 0.31 & 0.27 & 0.29 \\
+SNS & 0.60 & 0.57 & 0.59 & 0.32 & 0.28 &  0.29 \\
+tf-idf & 0.60 & 0.57 & 0.58 & 0.32 & 0.28 &  0.29 \\
+page rank & 0.36 & 0.34 & .35 & 0.12 & 0.10 &  0.11 \\
+CRP & 0.62 & 0.60 & 0.61 & 0.31 & 0.27 & 0.29 \\
 \midrule
 \emph{only with} &  &  &  &  &  &  \\ 
-SNS & x & x & x & 0.07 & 0.06 &  0.06 \\
-tf-idf & x & x & x & 0.08 & 0.07 &  0.07 \\
-page rank & x & x & x & 0.32 & 0.28 &  0.29 \\
-CRP & x & x & x & 0.08 & 0.07 &  0.07 \\
+SNS & 0.36 & 0.35 & 0.36 & 0.07 & 0.06 &  0.06 \\
+tf-idf & 0.22 & 0.21 & 0.22 & 0.08 & 0.07 &  0.07 \\
+page rank & 0.62 & 0.60 & 0.61 & 0.32 & 0.28 &  0.29 \\
+CRP & 0.21 & 0.20 & 0.21 & 0.08 & 0.07 &  0.07 \\
 \bottomrule

### 2015-08-21 paper.tex
- various small fixes

@@
 %opening
-\title{{\acronym} meets FOX: a combined approach to entity linking based on vector similarity }
-\titlerunning{{\acronym} meets FOX}
+\title{{\acronym}: a machine learning based approach to entity linking combining different features}
+\titlerunning{{\acronym}}
 
@@
 Given a named entity and a resource candidate, {\acronym} combines four features that quantify i) the likelihood that the actual name refers to the resource candidate (extracted from Wikipedia anchors), ii) the similarity of the textual context in which the name occurs to the textual context of the resource candidate (measured as the bag-of-words similarity using cosine), iii) the overlap between the semantic neighborhood signature of the resource candidate and the named entities mentioned in the larger context of the named entity, and iv) the prominence of the resource candidate as measured by its page rank in the DBpedia graph.
-An optimal non-linear model is trained using an SVM which combines these four features into an overall decision whether the named entity refers to a candidate resource or not.
+An optimal model is trained using an SVM which combines these four features into an overall decision whether the named entity refers to a candidate resource or not.
 
@@
 
-The input data for {\acronym} is a regular piece of text, for example a newspaper article, in which entity-representing sequences of tokens (\emph{fragments}) are already identified (we use the Stanford NER~\cite{ner}).
+The input data for {\acronym} is a regular piece of text, for example a newspaper article in which entity-representing sequences of tokens (\emph{fragments}) are already identified (we use the Stanford NER~\cite{ner}).
 For a given fragment, the algorithm's task is to determine the matching real-world entity.
@@
 
-Candidates are scored by a support vector machine.\footnote{{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four features are computed for each candidate, which are used as input for the SVM: tf-idf vector similarity, semantic neighborhood signature vector similarity, candidate reference probability, and page rank.
+Candidates are scored by a support vector machine.\footnote{For the training set the correct assignment and three randomly chosen false candidates for each entity are used.
+{\acronym} is using Weka's SMO: \url{http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMO.html}} Four features are computed for each candidate, which are used as input for the SVM: tf-idf vector similarity, semantic neighborhood signature vector similarity, candidate reference probability, and page rank.
 In the following we explain each of them in more detail.
@@
 % ------------ tf--idf vector similarity -------------------
-\subsection{tf-idf Vector Similarity}
+\subsection{tf-idf vector similarity}
 
@@
 Unfortunately, the input does not have a semantic neighborhood signature of its own.
-As a surrogate a candidate vector is generated as follows: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$.
+As a surrogate, a candidate vector is generated as follows: Let $m(e) \rightarrow c$ be a mapping from an entity $e$ to a count $c$.
 For each candidate entity of every fragment, check whether it already appears in the mapping.
@@
 
-$$\mathrm{crp}(a, e) := \frac{\mathrm{ref}(a, e)}{{\sum\limits_{a'\in E} \mathrm{ref}(a', e)}}$$
+$$\mathrm{crp}(a, e) := \frac{\mathrm{ref}(a, e)}{{\sum\limits_{a'\in A} \mathrm{ref}(a', e)}}$$
 
-Where $\mathrm{ref}(a, e)$ is the number of references from anchor/candidate $a$ to entity $e$ and $E$ is the set of all anchors referring to $e$.
+Where $\mathrm{ref}(a, e)$ is the number of references from anchor/candidate $a$ to entity $e$ and $A$ is the set of all anchors referring to $e$.
 
@@
 
-The idea behind the PageRank~\cite{pageRank} algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
+The idea behind the PageRank algorithm is to estimate the relevance of a website to a search query not only by whether the search terms appear on that page, but also by how many other pages were providing a hyperlink to the website in question.
 As DBpedia entries form a highly interconnected graph, the same principle can be applied in order to determine the page rank of a resource in DBpedia.
@@
 Notably the PageRank of a page is derived from the PageRank of its incoming links, meaning that the algorithm has to be iterated until the system reaches a steady state.
-The overall PageRank for a graph is supposed to be constant, but there are corner cases (like cycles) that have to be accounted for; see \cite{pageRank} for more information.
+The overall PageRank for a graph is supposed to be constant, but there are corner cases (like cycles) that have to be accounted for; see for more information.
 Our implementation uses the JUNG framework\footnote{Java Universal Network/Graph Framework: \url{http://jung.sourceforge.net/}}.
@@
 Table~\ref{table:redirects1} shows the evaluation results. 
-\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA/CoNLL dataset and achieves slightly worse but comparable results on the KORE50 dataset. 
+\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA/CoNLL dataset and achieves comparable results on the KORE50 dataset. 
 The latter is due to the fact that KORE50 was designed to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic neighborhood signature vector overlaps.
@@
 
+Table ~\ref{table:components} shows results leaving out single features and using only one feature. We clearly see that the page rank is the dominating factor. This deserves closer investigation.
+
 {\acronym} works best when a fragment refers to the most common meaning of a word.
@@
 tf-idf & 0.60 & 0.57 & 0.58 & 0.32 & 0.28 &  0.29 \\
-page rank & 0.36 & 0.34 & .35 & 0.12 & 0.10 &  0.11 \\
+page rank & 0.36 & 0.34 & 0.35 & 0.12 & 0.10 &  0.11 \\
 CRP & 0.62 & 0.60 & 0.61 & 0.31 & 0.27 & 0.29 \\
@@
 
-We have presented {\acronym}, a new entity linking approach that exploits a combination of features that are linearly combined using a Support Vector Machine.
-We have shown that the approach works very well when the contexts are longer, clearly outperforming FOX and DBpedia Spotlight on the AIDA CoNLL dataset.
-On the KORE50 dataset where contexts are shorter, it achieves comparable results to these approaches.
+We have presented {\acronym}, a new entity linking approach that exploits a combination of features that are combined using a Support Vector Machine.
+We have shown that the approach works very well when the input sentences are longer, clearly outperforming FOX and DBpedia Spotlight on the AIDA/CoNLL dataset.
+On the KORE50 dataset where sentences are shorter, it achieves comparable results to these approaches.
 In future work, we will release a service that can be publicly accessed using a similar interface to DBpedia Spotlight and FOX.
